{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-18 paper/paper.tex
added todos
added todo
added first sentences of the instantiation and the grammar of the assambly language

\begin{enumerate}
\item $Dom(next) = \{i \in \mathcal{P} | se(i) = high \land \exists j \in \mathcal{P} . i \mapsto^* j \land se(j) \neq high\}$ \todo{use simple method of new paper?}
\item $i, j \in Dom(next) \land i \mapsto j \Rightarrow next(i) = next(j)$
\item $i \in Dom(next) \land j \not\in Dom(next) \land i \mapsto j \Rightarrow next(i) = j$
\item $j, k \in Dom(next) \land i \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = next(k)$ \todo{is there an error?}
\item $i, j \in Dom(next) \land k \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = k$
\end{enumerate}

@@

\subsection{Instantiation}
\label{sec:instantiation}

>>>>

\todo{Use names from paper}
\begin{enumerate}
\item $Dom(next) = \{i \in \mathcal{P} | se(i) = high \land \exists j \in \mathcal{P} . i \mapsto^* j \land se(j) \neq high\}$ \todo{use simple method of new paper?}
\item $i, j \in Dom(next) \land i \mapsto j \Rightarrow next(i) = next(j)$
\item $i \in Dom(next) \land j \not\in Dom(next) \land i \mapsto j \Rightarrow next(i) = j$
\item $j, k \in Dom(next) \land i \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = next(k)$ \todo{is there an error?}
\item $i, j \in Dom(next) \land k \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = k$
\end{enumerate}

@@

\todo{What is wrong with property 4 (NeP3)}
\todo{What is wrong with property 5 (NeP4)}

\subsection{Instantiation}
\label{sec:instantiation}
To demonstrate how the framework can be used, it was instantiated with a simple
assembly language, which is given by the follow grammar:

\todo{beautify this}
\begin{align*}
instr &::= binop\ op && \text{binary operation with values from stack} \\
&|\ push\ n &&  \text{push value on the stack} \\
&|\ load\ x && \text{push value of variable on the stack} \\
&|\ store\ x && \text{store first element of the stack in x} \\
&|\ goto\ j\ |\ ifeq\ j && \text{un-/conditional jump to j} \\
&|\ start\ j && \text{create a new thread starting in j} \\
\end{align*}

where $op \in \{+,-,\times,/\}$, $n \in \mathbb{Z}$ and $x$ are variables. The
operational semantics are standard and not explicitly necessary for the following
instantiation, therefor they are omited.

The local states are modeled as a pair of the operand stack and the program counter. The
initial state $\lambda_{init}(pc)$ has an empty operand stack $\epsilon$ and points to
the given initial program point.

Besides this concrete language we need to define a type system to enforce noninterference
according to \ref{sec:typesystem}. The local types are defined by a stack of security levels
$LType = Stack(Level)$ and $t_{init}$ with the empty stack.
